---
title: 
output:
  bookdown::word_document2:
    reference_docx: C:/Users/allan/OneDrive/New_Graph/Current/Code/R/Templates/RMDTemplates/R/word_template.docx
    bibliography: references.bib
    toc: no
    fig_caption: yes
  bookdown::html_document2:
    number_sections: no
    self_contained: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=T, comment=NA, echo =FALSE, message=FALSE, warning=FALSE}
library(DBI)
library(tidyverse)
library(sf)
library(RPostgres)
library(data.table)
library(xlsx)
library(flextable)

#Enter the values for you database connection
conn <- dbConnect(
  RPostgres::Postgres(),
  dbname = 'postgis',
  host = 'localhost',
  port = 5432,
  user = 'postgres',
  password = 'postgres'
)

knitr::opts_chunk$set(echo=FALSE, comment=NA, message=FALSE, warning=FALSE, fig.align="center", fig.width = 5.118, fig.height = 3.409)
options(knitr.table.format = "html")


```

Rationale for sampling is to inform fish presence/absence and species composition/density as part of habitat confirmations to prioritize fish passage restoration at barrier culverts as per the Fish Passage Technical Working Group Phase 2 protocol
(https://www2.gov.bc.ca/gov/content/environment/natural-resource-stewardship/land-based-investment/investment-categories/fish-passage). Background planning and maps for the project is summarized in a 2018 report located at https://data.skeenasalmon.info/ar/dataset/fish-passage-site-prioritization-maps-bulkley-river. Additional information has been source from Gitxsan Watershed Authority and Wet'suwet'en fisheries.


Presence/absence of fish, species composition/density and distribution limits can be useful for prioritizing which crossings are a best fit for fish passage restoration and help inform follow up monitoring.  Sampling is proposed at a portion of the 15 - 20 or so sites we will be performing habitat confirmations at this summer.  The current list of candidate streams is extensive and will be narrowed down to under 30 in the next 5 weeks through modeling, ongoing communications with Wet'suwet'en, Skeena Fisheries Commission, DFO, Gitxsan Watershed Authority, FLNR and other stakeholders.


It is unlikely that sampling will be conducted at more than 10 of the streams listed in the sampling location tables however until the sites are visited in the field it is difficult to determine if the sampling will be beneficial to inform the prioritization and monitoring. Sampling methodologies will be dependent on the site, fish species suspected, type of habitat encountered and ongoing communications with numerous stakeholders but may include minnowtrapping, electrofishing, dipnetting and seining upstream and downstream of barrier culvert locations.


Please note that the sampling will be completed before September 30, 2020 however the period is listed as Dec 31, 2020 on the application to allow time outside of the busy field season for the data to be processed, QA'd and organized so that required reporting can be as informative as possible and submitted to the Province as per the permit conditions before 90 days has expired. 

I have attached an excel file with a complete list of potential sites, details and potential fish species encountered. Additionally, in response to a recomendation from David Dewit (Wet'suwet'en), I will be prepareing and submitting a letter seeking Wet’suwet’en consent for the work. Please don't hesitate to contact me if you have any questions or concerns at al@newgraphenvironment.com 2507771518.

```{r}
##bring in the priority info
# read the geopackage
df <- sf::st_read(
  "data/gis/fish_passage_skeena_20200714.gpkg",  ##this path does not work anymore b/c rmd files ref diff
  layer = "xings_bulk_morr_wet") %>% 
  mutate(long = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2]) %>% 
  sf::st_transform(crs = 3005) ##put in same crs as our moe layer

# add a unique id
df$misc_point_id <- seq.int(nrow(df))

# load to database
st_write(obj = df, dsn = conn, Id(schema= "working", table = "misc_points"))

# sf doesn't automagically create a spatial index or a primary key
res <- dbSendQuery(conn, "CREATE INDEX ON working.misc_points USING GIST (geom)")
dbClearResult(res)
res <- dbSendQuery(conn, "ALTER TABLE working.misc_points ADD PRIMARY KEY (misc_point_id)")
dbClearResult(res)

df_info <- dbGetQuery(conn, "SELECT a.misc_point_id, moe.region_name, wsg.watershed_group_code
FROM working.misc_points a
INNER JOIN whse_admin_boundaries.eadm_wlap_region_bnd_area_svw moe
ON ST_Intersects(a.geom, moe.geom)
                 INNER JOIN whse_basemapping.fwa_watershed_groups_poly wsg
                             ON ST_Intersects(a.geom, wsg.geom)")


##looks like everything is in the Skeena region and bulk or morr which makes sense.
#add the watershed group info because some are missing it (did not match modeled ids)

df <- left_join(
  select(df, -watershed_group_code),
  df_info,
  by = 'misc_point_id'
)

# table <- flextable::flextable(permit_table) %>%
#   # flextable::my_theme_booktabs(fontsize = 12, left_just_cols = 2) %>%
#   flextable::autofit() %>%
#   flextable::set_caption('Potential sampling site stream details.')
# table
```

```{r table-sites}
permit_table <- df %>% 
  mutate(stream_moe = as.character(stream_moe),
         stream_name_sfc = as.character(stream_name_sfc),
         stream_name = as.character(stream_name),
         waterbody = case_when(is.na(stream_moe) ~ stream_name_sfc,
                               T ~ stream_moe), 
         waterbody = case_when(is.na(waterbody) ~ stream_name,
                               T ~ waterbody)) %>% 
  mutate(comments = paste(comments_wetsuweten, comments_completion_details_sfc,
                               comments_moe),
         comments = stringr::str_replace_all(comments, 'NA', '')) %>% 
  select(MoE_region = region_name, waterbody, watershed_code_50k, watershed_code_20k,
         lat, long, uphab_gross_sub15_perc_km = uphab_gross_sub15_km, watershed_area_ha, upstr_species, comments,
         image_view_url, pscis_model_combined_id:map_ref_number_sfc, misc_point_id)


```

```{r}

fit_to_page_landscape <- function(ft, pgwidth = 12){
  
  ft_out <- ft %>% autofit()
  
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

table <- permit_table %>% 
  st_set_geometry(NULL) %>% 
  select(MoE_region:waterbody, lat, long, upstr_species,comments, misc_point_id) %>% 
  flextable::flextable() %>%
  # flextable::my_theme_booktabs(fontsize = 12, left_just_cols = 2) %>%
  # flextable::autofit() %>%
  flextable::set_caption('Potential sampling site stream details.') %>%
  flextable::width(j = 6, width = 2) %>% 
  flextable::fontsize(., size = 9, part = "all") %>% 
  fit_to_page_landscape()
table
```


```{r table-fish}
##find the gnis id
# watersheds <- dbGetQuery(conn,
#                          "SELECT y.* 
#                          FROM whse_basemapping.fwa_named_watersheds_poly y
#                          WHERE (y.gnis_name LIKE 'Parsnip River') ")


fish_species_watershed <- sf::st_read(conn,
                                      query = "SELECT nws.gnis_name,nws.fwa_watershed_code, nws.gnis_id, x.species_code,x.species_name,x.observation_date
                   FROM whse_fish.fiss_fish_obsrvtn_pnt_sp x
                   INNER JOIN 
                   whse_basemapping.fwa_named_watersheds_poly nws
                   ON ST_intersects(x.geom, nws.geom) 
                   WHERE gnis_name LIKE 'Bulkley River'
                           GROUP BY x.species_code,x.species_name,nws.gnis_name,nws.gnis_id,x.observation_date,nws.fwa_watershed_code 
                           ORDER BY nws.gnis_name,nws.fwa_watershed_code,x.species_code")

fish_species_lookup <- dbGetQuery(conn,
                                  "Select * from whse_fish.species_codes_lookup")

# fish_species_lookup <- drake::readd(fish_data_submission) %>% 
#                    purrr::pluck('species_by_group') %>% 
#                    select(common_name, species_code, scientific_name)


fish_species_watershed <- merge (fish_species_watershed,
                                fish_species_lookup[,c("SPECIES_CODE","SCIENTIFIC_NAME")],
                                by.x = c("species_code"), by.y = c("SPECIES_CODE"),
                                all.x = TRUE)

# fish_species_watershed <- left_join(fish_species_watershed,
#                                     fish_species_lookup,
#                                     by = "species_code") 


##we need to remove Family: from the SCIENTIFIC_NAME column to facilitate a nice sort/lookup
##we could look at adding it after in brackets maybe
# fish_species_watershed$scientific_name <- gsub("Family: ", "", fish_species_watershed$scientific_name)

##select rows that have no scientific name 
no_scientific <- fish_species_watershed[is.na(fish_species_watershed$scientific_name),]



#use pipes to group 
fish_table <- fish_species_watershed %>%
  purrr::set_names(nm = tolower(names(.))) %>% 
  dplyr::group_by(scientific_name, species_name,gnis_name,species_code) %>%
  dplyr::summarise(count = n()) %>%
  dplyr::arrange(gnis_name) %>% ##ditch the rare occurance which look like errors
  dplyr::filter(count > 1 & 
           # species_name != 'Dolly Varden' &
           species_name != 'Rainbow Smelt' &
           species_code != 'BT/DV' &
             species_code != 'AF' &
             species_code != 'OS' &
             species_code != 'SP' &
             species_code != 'TR' &
             species_code != 'LT' & ##just removing lake trout for this one
             !stringr::str_detect(species_name, "General")) %>%
  ungroup() %>% 
  select('Scientific Name' = scientific_name, 'Species Name' = species_name,
         'Species Code' = species_code) %>% 
  mutate_all(~replace_na(.,"-")) %>% 
  mutate_all(~stringr::str_replace_all(.,"NA", "-"))
  


table <- flextable::flextable(fish_table) %>%
  # flextable::my_theme_booktabs(fontsize = 12, left_just_cols = 2) %>%
  flextable::autofit() %>%
  flextable::set_caption('Fish species potentially encountered in Bulkley River watershed according to fisheries inventory summary records.')
table

```

```{r burn-xl}
write.xlsx2(as.data.frame(permit_table), file=paste0(getwd(), "/docs/permit_details.xlsx"), sheetName="sampling_locations", append=FALSE, row.names=FALSE)
##this one needs to come from the "01_modelled_Part3.... file
write.xlsx2(as.data.frame(fish_table), file="docs/permit_details.xlsx", sheetName="potential_species", append=TRUE, row.names=FALSE)
dbDisconnect(conn = conn)
```

